\chapter{Development Platforms and Tools}
\section{Hardware Tools }
Personal computers running windows or linux-based operating systems.

\section{Software Tools}
\subsection{Programming Languages}
\subsubsection{Python}
Python is a high-level programming language that is interpreted and object-oriented. It's ideal for Rapid Application Development, as well as using as a scripting or glue language to link together existing components.
\\
\textbf{Usage:} To build model and the web application

\subsubsection{Javascript}
Javascript is a scripting or programming language used to create and control dynamic website content, and it allows you to implement complex features on web pages.
\\
\textbf{Usage:} Used in web application for using image cropper.

\subsubsection{Dart}
Dart is an open-source, general-purpose, object-oriented programming language with C-style syntax developed by Google in 2011. Dart is designed for client development such as for the web, mobile apps, and also be used to build server and desktop applications.
\\
\textbf{Usage:} To build mobile application.

\subsection{Libraries and Frameworks}
\subsubsection{Tensorflow}
It is a symbolic math library, and is also used for machine and deep learning applications such as neural networks.
\\
\textbf{Usage:} For building our model based CNN.
\subsubsection{Keras}
Keras it is a software library that provides a Python interface for artificial neural networks.
\\
\textbf{Usage:} For testing and training our model based CNN.
\subsubsection{Numpy}
Numpy it is a library for Python programming language, adding support for large,
multi-dimensional arrays and matrices.
\\
\textbf{Usage:} For preparing the data for training process.
\subsubsection{OpenCV}
OpenCV it is a library of programming functions mainly aimed at real-time computer vision.
\\
\textbf{Usage:} For image preprocessing and segmentation.
\subsubsection{Flask}
Flask is a web framework, it’s a Python module that lets you develop web applications easily. It’s has a small and easy-to-extend core.
\\
\textbf{Usage:} For building web application and API.
\subsubsection{SQLite}
SQLite is a C-language library that implements a small, fast, self-contained, high-reliability, full-featured, SQL database engine.
\\
\textbf{Usage:} For building database.
\subsubsection{SQLAlchemy}
SQLAlchemy is the Python SQL toolkit and Object Relational Mapper that gives application developers the full power and flexibility of SQL.
\\
\textbf{Usage:} For storing and manipulating the database.
\subsubsection{Swagger}
Swagger is a set of open source tools for writing REST-based APIs. It simplifies the process of writing APIs by notches, specifying the standards and providing the tools required to write beautiful, safe, performant and scalable APIs.
\\
\textbf{Usage:} For documenting and handling APIs.
\subsubsection{Flutter}
Flutter is a free and open-source mobile UI framework created by Google and released in May 2017, it allows you to create a native mobile application with only one codebase.
\\
\textbf{Usage:} For building the mobile application.


\subsection{Tools and Platforms}
\begin{itemize}
    \item Jupyter Notebook: it is an interactive computational environment, in which you can combine code execution, rich text, mathematics, plots and rich media.
    \item PyCharm: it is a hybrid platform developed by JetBrains as an IDE for Python.
    \item Android Studio: it is the official IDE for Android app development, based on IntelliJ IDEA.
    \item GitHub: it is an online service that hosts Git repositories for software development and version control.
    \item AzureML: it is a cloud service for accelerating and managing the machine learning project lifecycle.
\end{itemize}


